A* with Perfect Potentials

### 2020-04-17 paper/ch_potentials.tex
add sketch of experiments section

>>>>

Tims plan:

\begin{itemize}
\item Effectiveness of A*
	\begin{itemize}
  \item Multiplied weights by 1 to 2 in steps of 0.05
  \item On DIMACs Eur
  \item Plot x factor, y running time
  \end{itemize}

\item Algo Building Blocks
	\begin{itemize}
  \item DIMACs Eur x1.1
  \item Table
  	\begin{itemize}
    \item columns: running time, potential evals, relaxed arcs
    \item rows: (Dijkstra, SCC, Deg2, Deg3) x (CH Pot or not)
    \item or transposed?
		\end{itemize}
	\end{itemize}

\item Applications
	\begin{itemize}
  \item Table
  	\begin{itemize}
    \item columns: running time, potential evals, relaxed arcs, shortest path distance / lower bound, dijkstra running time?
    \item rows: OSM Ger Mapbox Live, forbidden highways, forbidden tunnels, TD Ger06, TD Eur17, DIMACs Eur 1000 {Random|Fastest} Arcs {x2, x10}
		\end{itemize}
	\end{itemize}
\end{itemize}
